A 2-Norm Condition Number for B\'{e}zier Curve Intersection

### 2019-06-18 doc/paper.tex
Tweaking notation / LaTeX double quote in section 5.2.

One key argument for choosing Definition~\ref{defn:abstract-cond-num} over
the Highham condition number \(\kappa_H\) from~\eqref{eq:higham-cond-num} is
that \(\kappa_{\bm{\alpha}}\) is a natural extension of the condition number
for the equivalent one-dimensional problem. To see that this is so, we'll
define a "trivial" example by starting with a polynomial \(p(s)\) in Bernstein
form and a simple root \(\alpha\).

>>>>

One key argument for choosing Definition~\ref{defn:abstract-cond-num} over
the Highham condition number \(\kappa_H\) from~\eqref{eq:higham-cond-num} is
that \(\kappa_{\alpha, \beta}\) is a natural extension of the condition number
for the equivalent one-dimensional problem. To see that this is so, we'll
define a ``trivial" example by starting with a polynomial \(p(s)\) in Bernstein
form and a simple root \(\alpha\).
